Stable Neo-Hookean Flesh Simulation

### 2019-09-17 LaTeX-Master-Vorlage/chapter/paper.tex
working on structure in Energy
paper
working on paper illustration

\subsection{Previous Work}
Here comes previous work in neo-hookean energy formulation. What is neo-hookean and why do we need it here?

>>>>

\subsection{Previous Work}
Here comes previous work in neo-hookean energy formulation. What is neo-hookean and why do we need it here?
And what is wrong with each one.

\subsection{Stable Neo-Hookean Energy}
Conclude to the energy proposed in the paper.

\section{Energy Analysis}
Calculations and Herleitungen

\subsection{First Piola-Kirchhoff Stress (PK1)}
Explain.

\subsection{The Energy Hessian Terms}
Calculations

\subsection{The Tikhonov, Mu, and Gradient Terms}
Calculations

\subsection{The Volume Hessian}
Calculations

\subsection{The Complete Eigensystem}
Calculations

\section{Experiments with the Code}
The authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} kindly provided the implementation for an application of their formulated energy. In this code they implemented the stretch test on a cube. 
\\
The following images show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh.

\section{Discussion}
Stuff, Taylor approx.
